### 2017-03-23 paper/modes.tex
pass on sec2

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates relevant levels.  The highest
level indicates parallelism that can be obtained through different
machines on the network.  For instance, using virtual machines from a
cloud service to perform a distributed execution.  The machine space
sits under the ``network space'' and provides a \emph{lower-level}
parallelism.  In this case, computation can be offloaded at different
CPUs within a machine and at different threads within each CPU.  Note
that all these levels are complementary:  lower-level parallelization
schemes could leverage the computing power of server nodes in addition
to the aggregate processing power of the farm.

@@

This paper focuses at lower-level parallelism, which can be enabled
through build systems and testing frameworks.  Given the proliferation
of multi-core machines it is not surprising that testing frameworks
provide today support for parallel test execution (e.g.,
JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit}).
In the following we elaborate relevant features of and testing
frameworks build systems.  We focused on Java, Maven, and JUnit but
the discussion can be generalized to other language and tools.

@@

\begin{itemize}
\item
    \textbf{Sequential (\Seq).}~This configuration corresponds to the
        default behaviour in a test execution. No parallelism is
        involved.
\item
    \textbf{Sequential classes; parallel methods
        (\SeqClassParMeth{}).}~At this level of parallelism, the
        testing framework uses threads to run methods in parallel from
        the assigned test class. Each test class runs sequentially.
\item
    \textbf{Parallel classes; sequential methods
        (\ParClassSeqMeth{}).}~~At this level of parallelism, the
        testing framework uses threads to run classes in parallel and
        each test method runs sequentially within each thread.
\item
    \textbf{Parallel classes; Parallel methods
        (\ParClassParMeth).}~This configuration corresponds
        conceptually to the union of \ParClassSeqMeth{} and
        \SeqClassParMeth{}: the testing framework runs test methods
        from several classes in parallel.
\end{itemize}

Testing frameworks usually execute tests sequentially (\Seq{}) and may
allow the developer to use an ordering criteria (\eg, test name).  For
the \SeqClassParMeth{} setting, \Fix{elaborate and give example...}.
For the \ParClassSeqMeth{} setting, \Fix{elaborate and give
example...}. Finally, the \ParClassParMeth{} setting
\Fix{...elaborate...}.

@@

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={parallel, threadCount, perCoreThreadCount,
    forkCount, reuseFork},
    deletekeywords={true}
}
\begin{lstlisting}
<plugin>
    <groupId>org.apache.maven.plugins</groupId>
    <artifactId>maven-surefire-plugin</artifactId>
    <configuration>
        <forkCount>1C</forkCount>
        <reuseFork>true</true>
        <parallel>methods</parallel>
        <threadCount>1</threadCount>
        <perCoreThreadCount>true</perCoreThreadCount>
    </configuration>
</plugin>
\end{lstlisting}
    \caption{\label{fig:surefire} Maven configured with an
    \Fork{}\SeqClassParMeth{} setting: test methods run in parallel
    (\CodeIn{parallel} parameter) using two threads
    (\CodeIn{threadCount} parameter) per available core (flag
    \CodeIn{perCoreThreadCount}).}
\end{figure}

>>>>

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates relevant levels.  The highest
level indicates parallelism that can be obtained through different
machines on the network.  For instance, using virtual machines from a
cloud service to perform a distributed execution.  The machine space
sits under the ``network space'' and provides a \emph{lower-level}
parallelism.  In this case, computation can be offloaded at different
CPUs within a machine and at different threads within each CPU.  Note
that all these levels are complementary:  low-level parallelization
schemes could leverage the computing power of server nodes in addition
to the aggregate processing power of the farm.

@@

This paper focuses at low-level parallelism (\ie, machine and CPU
space), which can be enabled through build systems and testing
frameworks.  Given the proliferation of multi-core machines it is not
surprising that testing frameworks provide today support for parallel
test execution (e.g., JUnit~\cite{junit-org}, TestNG~\cite{testng},
and NUnit~\cite{nunit}).  In the following we elaborate relevant
features of and testing frameworks build systems.  We focused on Java,
Maven, and JUnit but the discussion can be generalized to other
language and tools.

@@

\begin{itemize}
\item
    \textbf{Sequential (\Seq).}~This configuration corresponds to the
        default behaviour in a test execution. No parallelism is
        involved.
\item
    \textbf{Sequential classes; parallel methods
        (\SeqClassParMeth).}~When running a test class, the testing
        framework executes methods on multiple threads. Each class
        runs sequentially.
\item
    \textbf{Parallel classes; sequential methods
        (\ParClassSeqMeth{}).}~The testing framework runs test classes
        on multiple threads and methods run sequentially within each
        thread.
\item
    \textbf{Parallel classes; Parallel methods
        (\ParClassParMeth).}~This configuration corresponds
        conceptually to the union of \ParClassSeqMeth{} and
        \SeqClassParMeth{}: the testing framework runs test methods
        from several classes on multiple threads.
\end{itemize}

Typically, testing frameworks executes tests in sequence by default
(\Seq{}) and may allow the developer to use an ordering criteria (\eg,
test name).  For the \SeqClassParMeth{} setting, \Fix{elaborate...}.
For the \ParClassSeqMeth{} setting, \Fix{elaborate...}. Finally, the
\ParClassParMeth{} setting \Fix{...elaborate...}.

@@

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={parallel, threadCount, perCoreThreadCount,
    forkCount, reuseFork},
    deletekeywords={true}
}
\begin{lstlisting}
<plugin>
    <groupId>org.apache.maven.plugins</groupId>
    <artifactId>maven-surefire-plugin</artifactId>
    <configuration>
        <forkCount>1C</forkCount>
        <reuseFork>true</true>
        <parallel>methods</parallel>
        <threadCount>5</threadCount>
    </configuration>
</plugin>
\end{lstlisting}
    \caption{\label{fig:surefire} Maven with a \ForkParMeth{}
    configuration. Maven forks one JVM per core (\CodeIn{forkCount}
    parameter) and \Jbc{check this $\rightarrow$} uses five threads
    (\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
    parameter) within each test class.}

%%    test methods run in parallel (\CodeIn{parallel}
%%    parameter) using two threads (\CodeIn{threadCount} parameter) per
%%    available core (flag \CodeIn{perCoreThreadCount}).}
\end{figure}
